毕业设计论文

### 2010-06-18 doc/paper/mypaper.tex
论文定稿

Web服务器作为互联网的核心组成部分，在支撑整个互联网服务中，起到了至关重要的作用。由于互联网中应用的不断更新，要求web服务器也能适应这种更新变化。同时，web服务器必须保证7*24小时的运行。在目前的正在使用的web服务器中，大部分都不支持功能的动态增加，也就是在不重启服务器的情况下，动态的为服务器增加功能。针对这一问题，本课题基于动态链接库技术，使服务器在运行期间，可以动态的获知模块的增加并加载模块。

本论文的主要内容是研究实现基于动态链接技术的Web服务器动态加载插件的接口。首先，文中介绍了本课题的背景和意义，以及作者的主要任务和工作。接着概述与本课题相关的HTTP协议（RFC2616）的内容，简单介绍动态链接技术及其使用，还有介绍Web服务器的一些主流设计和实现方法。接下来，通过对HTTP协议的分析，设计插件的接口，分析动态链接技术，设计动态加载插件的过程。然后，采用非阻塞I/O+线程池+I/O多路复用技术，设计服务器的架构。然后，根据以上的设计，在Linux系统下，实现服务器的原型，并在其上实现插件接口和动态加载功能。本系统实现了服务器的基本功能，重点实现模块动态加载特性，并对实现进行测试。

@@

\enabstract
	As the core component of the Word Wide Web, the web sever acts as a very important role to support the whole internet service. Due to the continuous update of the internet application, the web server must adapt this update. At the same time, the web server must keep running 7 * 24 hours. In the web servers which are used now, all most of them do not support to dynamically adding functions. Namely, when the server is running and dose not reboot, we can add new function to the server. Against this problem, this issue let the web servers can be added new function plugin or deleted function plugin when they are running based on dynamic link technology.

	The main content of this paper is that studying the interface of dynamically loading function of the web sever based on dynamic link technology. First, the paper introduces the background and significance of this issue and the main task and job of the author. Then, the paper outlines the HTTP protocol(RFC 2616) and the dynamic link technology and its application, also outlines some design and implement methods of the web server. Next, by analysising the HTTP protocol and the dynamic link technology, we design the interface of the plugin and the process of dynamically loading the function plugin. Then, using nonblocking I/O, thread pool and I/O multiplexing, we design the architecture of the web server. Last, according to the designs above, we implement a prototype of the web server and implement the interface of the plugin and dynamically loading on it on the Linux system.This system implements the base functions of the web server and focuses on the implementation of the feature of dynamically loading function and testing the implementation.

@@

\section{课题目标及作者的主要工作}
	本课题通过分析HTTP协议（RFC2616）,设计插件所需的接口，通过使用动态链接技术，设计插件的动态加载的过程。最后，通过使用非阻塞I/O，I/O多路复用以及线程池的技术，构造出一个简单的Web服务器，并在这个服务器上验证插件接口的设计。最终，服务器将能完成基本的HTTP协议解析和处理，正确的加载和调用插件。

	\vspace{12pt}
	主要工作：
	\begin{enumerate}
		\item 学习动态链接库和web服务器设计实现的相关知识和技术                                
		\item 技术可行性论证，需求分析，构造系统结构                                            
		\item 搭建开发环境，编码实现 
		\item 测试插接接口的额可用性和服务器的性能                                                                                              
		\item 撰写毕业设计论文                                                                  
		\item 查找外文文献并翻译 
	\end{enumerate}

@@

	\begin{figure}[t]
	\centering
	\caption{开门关门状态机\ucite{wiki}}
	\label{fsm}
	\includegraphics[height=8cm, width=6cm]{pics/fsm.eps}
	\end{figure}

@@

@@

@@

	\begin{figure}[t]
	\centering
	\setlength{\abovecaptionskip}{0pt}
	\setlength{\belowcaptionskip}{10pt}
	\caption{服务器启动}
	\label{startup}
	\includegraphics[height=6cm, width=15cm]{pics/startup.eps}
	\end{figure}

@@

	加载插件的日志。如图\ref{loadpluginlog}。

@@

	测试结果总结如表\ref{testingresult}
	\begin{table}[t]
	\caption{测试结果：}
	\label{testingresult}
	\centering
	\begin{tabularx}{\textwidth}{p{1cm}XXXXl} %最后一列是空的。这样可以是倒数第二列居中，否则会报错或不居中。
	\toprule
	\centering 序号 & \centering  测试内容 & \centering  测试结果 &\centering 实际运行结果&\centering 是否符合要求&\\
	\midrule
	\centering 1 &\centering 启动并监听端口 &\centering 成功启动和监听端口 &\centering 成功启动和监听端口 & \centering 符合&\\
	\centering 2 &\centering 处理客户端请求 &\centering 返回请求资源 &\centering   返回请求资源& \centering 符合&\\
	\centering 3 &\centering 动态加载插件 &\centering  加载成功 &\centering  加载成功& \centering 符合&\\
	\centering 4 &\centering 调用插件 & \centering 正确调用插件 & \centering 正确调用插件& \centering 符合&\\
	\centering 5 &\centering 卸载插件 &\centering  卸载成功 &\centering  卸载成功& \centering 符合&\\
	\bottomrule
	\end{tabularx}
	\end{table}

@@

\section*{Related Sites}

In October 2003, Felix von Leitner put together an excellent web page and presentation about network scalability, complete with benchmarks comparing various networking system calls and operating systems. One of his observations is that the 2.6 Linux kernel really does beat the 2.4 kernel, but there are many, many good graphs that will give the OS developers food for thought for some time. (See also the Slashdot comments; it'll be interesting to see whether anyone does followup benchmarks improving on Felix's results.)

\section*{Book to Read First}

If you haven't read it already, go out and get a copy of Unix Network Programming : Networking Apis: Sockets and Xti (Volume 1) by the late W. Richard Stevens. It describes many of the I/O strategies and pitfalls related to writing high-performance servers. It even talks about the 'thundering herd' problem. And while you're at it, go read Jeff Darcy's notes on high-performance server design.

(Another book which might be more helpful for those who are *using* rather than *writing* a web server is Building Scalable Web Sites by Cal Henderson.)

@@

\section*{Comments}

Richard Gooch has written a paper discussing I/O options.

In 2001, Tim Brecht and MMichal Ostrowski measured various strategies for simple select-based servers. Their data is worth a look.

In 2003, Tim Brecht posted source code for userver, a small web server put together from several servers written by Abhishek Chandra, David Mosberger, David Pariag, and Michal Ostrowski. It can use select(), poll(), epoll(), or sigio.

Back in March 1999, Dean Gaudet posted:

I keep getting asked "why don't you guys use a select/event based model like Zeus? It's clearly the fastest." ...

His reasons boiled down to "it's really hard, and the payoff isn't clear". Within a few months, though, it became clear that people were willing to work on it.

Mark Russinovich wrote an editorial and an article discussing I/O strategy issues in the 2.2 Linux kernel. Worth reading, even he seems misinformed on some points. In particular, he seems to think that Linux 2.2's asynchronous I/O (see F\_SETSIG above) doesn't notify the user process when data is ready, only when new connections arrive. This seems like a bizarre misunderstanding. See also comments on an earlier draft, Ingo Molnar's rebuttal of 30 April 1999, Russinovich's comments of 2 May 1999, a rebuttal from Alan Cox, and various posts to linux-kernel. I suspect he was trying to say that Linux doesn't support asynchronous disk I/O, which used to be true, but now that SGI has implemented KAIO, it's not so true anymore.

See these pages at sysinternals.com and MSDN for information on "completion ports", which he said were unique to NT; in a nutshell, win32's "overlapped I/O" turned out to be too low level to be convenient, and a "completion port" is a wrapper that provides a queue of completion events, plus scheduling magic that tries to keep the number of running threads constant by allowing more threads to pick up completion events if other threads that had picked up completion events from this port are sleeping (perhaps doing blocking I/O).

See also OS/400's support for I/O completion ports.

There was an interesting discussion on linux-kernel in September 1999 titled "> 15,000 Simultaneous Connections" (and the second week of the thread). Highlights:

\begin{itemize}
\item Ed Hall posted a few notes on his experiences; he's achieved >1000 connects/second on a UP P2/333 running Solaris. His code used a small pool of threads (1 or 2 per CPU) each managing a large number of clients using "an event-based model".
\item Mike Jagdis posted an analysis of poll/select overhead, and said "The current select/poll implementation can be improved significantly, especially in the blocking case, but the overhead will still increase with the number of descriptors because select/poll does not, and cannot, remember what descriptors are interesting. This would be easy to fix with a new API. Suggestions are welcome..."
\item Mike posted about his work on improving select() and poll().
\item Mike posted a bit about a possible API to replace poll()/select(): "How about a 'device like' API where you write 'pollfd like' structs, the 'device' listens for events and delivers 'pollfd like' structs representing them when you read it? ... "
\item Rogier Wolff suggested using "the API that the digital guys suggested", \\http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps
\item Joerg Pommnitz pointed out that any new API along these lines should be able to wait for not just file descriptor events, but also signals and maybe SYSV-IPC. Our synchronization primitives should certainly be able to do what Win32's WaitForMultipleObjects can, at least.
\item Stephen Tweedie asserted that the combination of F\_SETSIG, queued realtime signals, and sigwaitinfo() was a superset of the API proposed in http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps. He also mentions that you keep the signal blocked at all times if you're interested in performance; instead of the signal being delivered asynchronously, the process grabs the next one from the queue with sigwaitinfo().
\item Jayson Nordwick compared completion ports with the F\_SETSIG synchronous event model, and concluded they're pretty similar.
\item Alan Cox noted that an older rev of SCT's SIGIO patch is included in 2.3.18ac.
\item Jordan Mendelson posted some example code showing how to use F\_SETSIG.
\item Stephen C. Tweedie continued the comparison of completion ports and F\_SETSIG, and noted: "With a signal dequeuing mechanism, your application is going to get signals destined for various library components if libraries are using the same mechanism," but the library can set up its own signal handler, so this shouldn't affect the program (much).
\item Doug Royer noted that he'd gotten 100,000 connections on Solaris 2.6 while he was working on the Sun calendar server. Others chimed in with estimates of how much RAM that would require on Linux, and what bottlenecks would be hit.
\end{itemize}
Interesting reading!

@@

\section*{相关的网站}

	在2003年十月，Felix von Leitner集中了一个优秀的网页并展示了关于网络的可扩展性，完成了比较不同网络系统调用和操作系统的基准。他的其中之一的结论就是Linux2.6内核完全击败了Linux2.4内核，同样，也有许多好的图表可以提供给操组系统开发者很好的思想源泉。（参看Slashdot的注解。看看一些人是怎样做后续基准程序来提高Felix的结果是非常有意思的。）

\section*{要先看的书}

	如果你还没有读过W. Richard Stevens的Unix网络编程：网络API：套接字联网（卷一），去读一遍吧。书中描述了很多关于编写高性能服务器的I/O策略和陷阱。书中甚至讨论'thundering herd'问题。如果你读完了，去看Jeff Darcy关于高性能服务器设计的札记。
（另一本Cal Henderson的构建可扩展的web站点（Building Scalable Web Sites）对那些用web服务器而不是写服务器的人更有帮助。）

@@

\section*{注解}
	Richard Gooch写了一篇讨论I/O选项的论文。

	在2001年，Tim Brecht和MMichal Ostrowski测量了各种策略下的简单基于select服务器的性能。他们的数据值得一看。

	在2003年，Tim Brecht发布了userver的源代码。这是一个下的web服务器，集合了Abhishek Chandra，David Mosberger，David Pariag和Michal Ostrowski所写的多个服务器。它可以使用select()，poll()，epoll()或者sigio。

	回到1999年五月，Dean Gaudet发帖说：

	我不断地被问道“为什么你们这些人不使用基于select/event的模型，就像Zeus？很明显那是最快的。”...

	他的理由归结为“很困难，并且回报不明显”。但是几个月后，越来越明显，人们喜欢使用它。

	Mark Russinovich写了一篇社论和论文讨论关于Linux2.2内核的I/O策略。值得一读，虽然他似乎乎略了一些观点。实际上，他似乎认为Linux2.2内核的异步I/O（参见上文F\_SETSIG）不会在数据准备就绪时通知用户进程，而是仅仅在新连接到达时通知。这看起来是一个异乎寻常的误解。参见一个早期草案的注解，Ingo Molnar在1999年4月30日的反驳，Russinovich在1999年5月2日的注解，Alan Cox的反驳和linux-kernel的帖子。我猜测他试图在说Linux不支持异步磁盘I/O，这个曾经确实是对的。但是现在，SGI已经实现了KAIO，这个不在是对的了。

	参见这些关于“完成端口”的sysinternals.com和MSDN的网页。他认为完成端口是NT特有的。总之，win32的“覆盖I/O”过于底层而不方便使用，并且一个“完成端口”是一个包装，提供了完成事件的队列，外加通过当别的已经从这个端口获得完成事件的线程处于睡眠状态时（可能在做阻塞I/O）， 允许更多更多的线程获得完成事件来保持运行状态的线程数量保持不变。

	参见OS/400的对完成端口的支持。

	1999年9月，在linux-kernel上有一个内部的讨论，“>15000并发连接”（线程的第二个星期）。主要包括：

	\begin{itemize}
		\item Ed Hall发布了一些关于他的经验的手记。他的在一个运行Solaris的HP P2/333上实现>1000 个连接/秒的方案。他的代码使用了一个小的线程池（1或2个每个CPU）每个线程处理大量客户端使用“一个基于事件的线程”。
		\item Mike Jagdis发布了一个关于poll/select开销的分析，他说“当前的select/poll实现可以被显著的提高，尤其是在阻塞的情况下。但是开销依然会随着描述符数量的增加而增加，这是因为select/poll没有，也不可能记住哪些描述符可能有事件。这个很容易通过一个新的API来修正。欢迎提建议...”
		\item Mike发布了他的关于提高select()和poll()性能的工作。
		\item Mike发布了一点关于一个可能替换select()/poll()的API：“在一写‘类pollfd’结构体的地方，一个‘类设备’的API如何，这个‘设备’监听事件并且在你读它的时候，它传送‘类pollfd’结构体来表示事件？...”
		\item Rogier Wolff建议使用“数字开发人员建议的API”，http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps
		\item Joerg Pommnitz指出，这个讨论中的任何新的API必须不仅仅能构等待文件描述符的事件，还要能够等待信号和也许SYSV-IPC。至少，我们的同步原语能够确切的完成Win32的WaitForMultipleObjects能够完成的任务。
		\item Stephen Tweedie断言，F\_SETSIG，实时信号队列和sigwaitinfo()的组合是http://www.cs.rice.edu/\~gaurav/papers/usenix99.ps所提到的API的超集。他还提到，如果你很在意效率，那么一致保持信号阻塞。否则，进程从sigwaitinfo()的队列中抓取下一个信号，而不是异步的传送信号。
		\item Jayson Nordwick比较了完成端口和F\_SETSIG同步事件模型，得出的结论是他们非常的相似。
		\item Alax Cox指出，一个旧的SCT的SIGIO的rev补丁包含在2.3.18ac中。
		\item Jordan Mendelson发布了一些如何使用F\_SETSIG的示例代码。
		\item Stephen C. Tweedie继续比较了完成端口和F\_SETSIG，指出“当使用一个信号队列机制时，如果正在使用的库也使用了相同的机制，那么，你的程序将获得那些本来属于各种库组件的信号。”但是，库可以设置自己的信号处理函数，因此这个不会（过多）的影响程序。
		\item Doug Royer指出，当他在Sun日期服务器上工作的时候，他获得了100000个连接在Solaris2.6上。其他的关于如何估计在Linux需要多少RAM和将会遇到什么瓶颈的文章。
	\end{itemize}

	有趣的文章！

>>>>

Web服务器作为互联网的核心组成部分，在支撑整个互联网服务中，起到了至关重要的作用。由于互联网中应用的不断更新，要求web服务器也能适应这种更新变化。同时，web服务器必须保证7*24小时的运行。在目前的正在使用的web服务器中，大部分都不支持功能的动态增加，也就是在不重启服务器的情况下，动态的为服务器增加功能。
本论文的主要内容是研究实现基于动态链接技术的Web服务器动态加载插件的接口。首先，文中介绍了本课题的背景和意义，以及作者的主要任务和工作。接着概述与本课题相关的HTTP协议（RFC2616）的内容，简单介绍动态链接技术及其使用，还有介绍Web服务器的一些主流设计和实现方法。接下来，通过对HTTP协议的分析，设计插件的接口，分析动态链接技术，设计动态加载插件的过程。然后，采用非阻塞I/O+线程池+I/O多路复用技术，设计服务器的架构。本系统实现了服务器的基本功能，重点实现模块动态加载特性，并对实现进行测试。

@@

\enabstract
	As the core component of the Word Wide Web, the web sever acts as a very important role to support the whole internet service. Due to the continuous update of the internet application, the web server must adapt this update. At the same time, the web server must keep running 7 * 24 hours. In the web servers which are used now, all most of them do not support to dynamically adding functions. Namely, when the server is running and dose not reboot, we can add new function to the server.

	The main content of this paper is that studying the interface of dynamically loading function of the web sever based on dynamic link technology. First, the paper introduces the background and significance of this issue and the main task and job of the author. Then, the paper outlines the HTTP protocol(RFC 2616) and the dynamic link technology and its application, also outlines some design and implement methods of the web server. Next, by analysising the HTTP protocol and the dynamic link technology, we design the interface of the plugin and the process of dynamically loading the function plugin. Then, using nonblocking I/O, thread pool and I/O multiplexing, we design the architecture of the web server. This system implements the base functions of the web server and focuses on the implementation of the feature of dynamically loading function and testing the implementation.

@@

\section{课题目标及作者的主要工作}
	\subsection{课题目标}
	本课题通过分析HTTP协议（RFC2616）,设计插件所需的接口，通过使用动态链接技术，设计插件的动态加载的过程。最后，通过使用非阻塞I/O，I/O多路复用以及线程池的技术，构造出一个简单的Web服务器，并在这个服务器上验证插件接口的设计。最终，服务器将能完成基本的HTTP协议解析和处理，正确的加载和调用插件。

%	\vspace{12pt}
	\subsection{作者主要工作}
	\begin{enumerate}
		\item 学习动态链接库和web服务器设计实现的相关知识和技术                                
		\item 技术可行性论证，需求分析，构造系统结构                                            
		\item 搭建开发环境，编码实现 
		\item 测试插接接口的额可用性和服务器的性能                                                                                              
		\item 撰写毕业设计论文                                                                  
	\end{enumerate}

@@

	\begin{figure}[htbp]
	\centering
	\caption{开门关门状态机\ucite{wiki}}
	\label{fsm}
	\includegraphics[height=8cm, width=6cm]{pics/fsm.eps}
	\end{figure}

@@

	当服务器检测到了配置文件的修改之后，服务器执行下面的函数完成插件的加载。这个函数被注册到I/O多路复用系统中，有多路复用系统在检测到配置文件修改后调用。

	\begin{verbatim}
static handler_t plugin_conf_inotify_fdevent_handler(
				void *srv, void *ctx, int revents)
{
	server *s = (server*)srv;
	conf_inotify *ity = (conf_inotify*)ctx;
	//分配存储空间ity-> buf
	...

	int rlen, offset = 0;
	int read_done = 0;
	while(!read_done)
	{
		if(-1 == (rlen = read(ity -> fd, ity -> buf + offset
			, ity -> buf_len - offset))){
			...
		}
		else{
			offset += rlen;
		}
	}
	int tmp_len;
	struct inotify_event *e;
	for(tmp_len = 0; tmp_len < offset; )
	{
		e = (struct inotify_event *)(ity -> buf + tmp_len);
		if(e -> wd == ity -> plugin_conf_wd)
		{
			if(e -> mask & IN_CLOSE_WRITE)
			{
				pthread_mutex_lock(&s -> plugin_lock);
				plugin_free(s);
				pthread_mutex_unlock(&s -> plugin_lock);
				plugin_load(s);
			}
			break;
		}
		tmp_len += sizeof(int); 			
		tmp_len += 3 * sizeof(uint32_t);	
		tmp_len += e -> len;
	}

	return HANDLER_FINISHED;
}
	\end{verbatim}
	在函数中，通过read从inotify系统中读取发生的修改事件，判断所发生的事件是不是IN\_CLOSE\_WRITE。最后，释放以前加载的所有插件，调用plugin\_load重新加载所有的插件，包括新增加的。

@@

	http\_prepare\_response函数的框架如下：
	\begin{verbatim}
handler_t http_prepare_response(server *srv, connection *con)
{
	handler_t ht;
	/*
	 * 在此处，函数对uri地址进行解析。  
	 * 将解析好的uri地址存放在con -> uri中。
	 */
	...
	//得到没有解码的url地址。调用插件。
	switch(ht = plugin_handle_url_raw(srv, con))
	{
		case HANDLER_GO_ON:
			break;
		case HANDLER_FINISHED:
			return ht;
		default:
			break;
	}
	//解码url地址和query数据。
	...
	//解码url地址。调用插件。
	switch(ht = plugin_handle_url_clean(srv, con))
	{
		case HANDLER_GO_ON:
			break;
		case HANDLER_FINISHED:
			return ht;
		default:
			break;
	}
	//设置连接处理时的默认根目录。
	buffer_copy_string_buffer(con -> physical.doc_root
	, srv -> srvconf.docroot);

	//有些插件需要设置工作根目录。
	...
	//此处函数拼接物理地址。
	...
	//得到物理地址。 调用插件。
	...
	//检查所请求的资源是否存在。
	...
	//处理子请求
	...
	//处理静态页面。
	...
	return HANDLER_ERROR;
}
	\end{verbatim}
	上面的代码省略了对request请求的处理过程，着重突出插件接口的调用时机。由这个函数的实现可以看出，插件接口的调用都有固定的时机。当服务器需要增加功能时，只需要根据功能的特定，实现相应的接口函数即可。

@@

	\begin{figure}[htbp]
	\centering
	\setlength{\abovecaptionskip}{0pt}
	\setlength{\belowcaptionskip}{10pt}
	\caption{服务器启动}
	\label{startup}
	\includegraphics[height=6cm, width=15cm]{pics/startup.eps}
	\end{figure}

@@

	加载插件的日志。如图\ref{loadpluginlog}。从日志中我们可一看到，服务器检测到了配置文件的修改。接着，服务器重新读取了配置文件，然后加载插件。日志中还显示了插件所实现的结构。可以看到，插件实现了三个接口，服务器获得了所实现接口函数的入口地址。

@@

	测试结果总结如表\ref{testingresult}
	\begin{table}[htbp]
	\caption{测试结果：}
	\label{testingresult}
	\centering
	\begin{tabularx}{\textwidth}{p{1cm}XXXXl} %最后一列是空的。这样可以是倒数第二列居中，否则会报错或不居中。
	\toprule
	\centering 序号 & \centering  测试内容 & \centering  测试结果 &\centering 实际运行结果&\centering 是否符合要求&\\
	\midrule
	\centering 1 &\centering 启动并监听端口 &\centering 成功启动和监听端口 &\centering 成功启动和监听端口 & \centering 符合&\\
	\centering 2 &\centering 处理客户端请求 &\centering 返回请求资源 &\centering   返回请求资源& \centering 符合&\\
	\centering 3 &\centering 动态加载插件 &\centering  加载成功 &\centering  加载成功& \centering 符合&\\
	\centering 4 &\centering 调用插件 & \centering 正确调用插件 & \centering 正确调用插件& \centering 符合&\\
	\centering 5 &\centering 卸载插件 &\centering  卸载成功 &\centering  卸载成功& \centering 符合&\\
	\bottomrule
	\end{tabularx}
	\end{table}

@@

@@

@@

@@
